\huge{A Strategy-Proof Budget Feasible Online Mechanism for Crowdsensing with Time-Discounting Values}

### 2016-11-13 paper.tex
bib

Mobile crowdsensing is a novel application paradigm that utilizes mobile devices to collect, analyze, and share their local information~\cite{ganti2011mobile,lane2010survey}. It usually consists of a service provider, service requesters, and mobile device users. The service provider (a.k.a., the crowdsensing platform), which usually resides in the cloud, recruits participants from mobile device users to upload their sensing data, and then provides services to service requesters based on the collected information. A wide variety of applications has emerged in recent years, including NoiseTube and Ear-phone~\cite{maisonneuve2009noisetube,rana2010ear} for noise monitoring, SignalGuru and CrowdAtlas~\cite{koukoumidis2011signalguru,wang2013crowdatlas} for traffic monitoring, and CrowdPark, Parknet~\cite{yan2011crowdpark,mathur2010parknet} for finding on-street parking spots.

Since participating in crowdsensing tasks requires the participants to devote resource consumptions of their smartphones, participants are usually reluctant to share their sensing capabilities. Thus, it is necessary to design an incentive mechanism to compensate the participants. According to different settings of scenarios, two cases are often discussed, \ie, offline setting and online setting. Researches on incentive mechanism designs, such as~\cite{yang2012crowdsourcing,koutsopoulos2013optimal}, are usually based on offline scenarios, where participants are present simultaneously while the online scenarios are more common in practice, where participants arrive and leave dynamically. Designing an incentive mechanism in online scenarios is much more complicated, due to the lack of future information. Besides, it brings challenges in the realization of strategy-proofness, since participants may misreport their arrival or departure time in order to gain higher benefits. Here, intuitively, strategy-proofness means that one can maximize her benefit by truthfully revealing her private information (\eg, arrival time, departure time, or sensing cost).

@@

We note that most existing works on online mechanism design only consider flat values, \ie, the value of each participant's contributed data is fixed during her presence. However, in many time sensitive applications (\eg, real-time traffic or noise monitoring), the participants usually have time-discounting values \cite{babaioff2009secretary, wu2014strategy}, \ie, the value of each participant's contribution decreases as time goes by. The time-discounting property really complicates the mechanism design problem. For instance, it has been proved that no online algorithm can achieve a competitive ratio better than $\Omega(\textrm{log}n/\textrm{log}\,\textrm{log}n)$ for discounted secretary problem~\cite{babaioff2009secretary}.

@@

To address these challenges, we propose a budget feasible online incentive mechanism with time-discounting values. We first consider the case where the total value is the summation of each participant's value. We define the efficiency of a participant as her value divided by her cost. Since participants arrive dynamically, we take advantage of the efficiency information of those who have arrived (we call a sample set) to calculate a threshold, and use it to guide subsequent selections. The intuition of our design is to greedily choose participants with the highest efficiencies from the sample set, and calculate their average efficiency multiplying an increasing factor as a threshold. The increasing factor is used to prevent the participants from misreporting their arrival or departure time. We divide the total time into slots. At each time slot, we select participants with efficiencies higher than the threshold within the budget constraint, and then calculate their payments. The payment scheme is carefully designed to ensure strategy-proofness and individual rationality. We prove that our mechanism can achieve a constant competitive ratio compared with the optimal solution with full information. We next consider the case where the total value is a submodular function of the selected participants, which is a more general situation. We prove that the time and cost-truthfullness can still be guaranteed by the newly designed algorithms. The numerical results show that our proposed approach has superior performance to our benchmark mechanisms.

The rest of the paper is organized as follows. We briefly review the related work in Section II. In Section III, We introduce the model of the budget feasible online mechanism problem with time-discounting values, and recall some important solution concepts. In Section IV, we present our design of a strategy-proof online  mechanism where the value function is the summation of each participant's value. In Section V, we consider the case where the value function submodular. In Section VI, we implement and evaluate our mechanism. Finally, we conclude this paper in Section VI.
%**********************************************************
%The key challenges in a budget feasible auction are how to persue the maximum value and balance incentive compatibility and the budget constraint. It gets harder when the participants arrive dynamicly. What is noticeable is that in existing works, the value of a specific participant is often fixed, \ie, the participant has a bid of uniform value during her presence in the auction, independent of when she is selected. But in some realms, such as applications intending to collect data by crowdsensng, which are always modeled as reverse auctions, the values of participants' contributed information decrease with time. The time discounting characteristic can make the problem more difficult. In this paper, we study a type of online reverse auction, where the participants compete to provide items or services with certain time discounting values. Then the provider gives some payment to the selected participants according to their bids. The objective is to obtain  the maximum total value and achieve strategy-proofness under a limited budget. It should be noted that for general utility functions, there is no truthful mechanism achieving a reasonable approximation ratio~\cite{singer2014budget}. In our paper, the total value of participants is simplified to the summation of their values at when they are selected.
%**********************************************************
%We present a formal methonology based on the mechanism design as an inventive method in the realm of crowdsensing. which is a new paradigm of applications that includes a platform and ubiquitous participants who hold mobile devices equipped with enhanced sensors~\cite{ganti2011mobile}. The platform recruits participants to upload sensing data and then compensate them some payment according to their value. It is always modeled as a reverse auction. When designing an incentive mechanism for crowdsensing, participants' value is often taken into account when determining the task allocation and the payment. But in existing work, this value of a specific participant is often fixed, \ie, the participants have a bid of uniform value to the platform during their presences in the auction. However in many crowdsensing applications, the value of participants is time discounting, decreasing with time in majority situations. Therefore in this paper, we consider a scenario, in which participants compete for being allocated tasks and then compensated some monetary payment, but her bidding value is changing over time.  The bid of each participant is her arrival time, departure time, her cost and value to the platform which diminishes with time. The objective is to design a strategy-proof mechanism and maximize the platform's gainning value with limited budget with respect to not only the time discounting values, but also the present time and cost of the participants.

@@

The budget feasible mechanism has been widely studied to address budget limited mechanism design problem. Singer~\cite{singer2010budget} first designed a budget feasible mechanism for scenarios where the value function is submodular. Chen \et\cite{chen2011approximability} further proposed a truthful budget feasible mechanism. It achieves a competitive ratio of larger than $\frac{1}{9}$, which is better than previously best result 233.83. Nevertheless, these work also failed to consider the time-discounting property.
%Zhou \et\cite{zhou2008budget} modeled the budgeted bidding optimization problem as an online knapsack problem, where the threshold is calculated based on the fraction of capacity filled.

Furthermore, there are some loosely related works on online mechanism design, \eg,  pricing and resource allocation in cloud computing~\cite{Shi:2014:OAF:2591971.2591980}, allocating tasks with temporal constraints~\cite{nunes2015multi}, improving targeting to increase total revenue~\cite{Hummel:2015:ITI:2736277.2741079}, and dynamic resource bundling and VM provisioning in IaaS clouds~\cite{Zhang:2015:OAI:2796314.2745855}.

@@

\begin{table}[!hbp]
\center
\begin{tabular}{|c|c|}
\hline

Symbol & Description\\
\hline
$\mathbb{N}={1,2,...,n}$ & The participant set \\
\hline
$B$ & The total budget\\
\hline
$\theta_i$ & Type of participant $i$\\
\hline
$a_i$ & arrival time of participant $i$\\
\hline
$d_i$ & departure time of participant $i$\\
\hline
$v_i$ & value of participant $i$\\
\hline
$c_i$ & cost of participant $i$\\
\hline
$\hat{\theta}_i$ & bid of participant $i$\\
\hline
$\mathbb{T}=\{1,2,...,T\}$ & the time slot set\\
\hline
$\beta$ & time-discounting factor\\
\hline
$p_i$ & payment of participant $i$\\
\hline
$\mathbb{S}$ & selected participant set\\
\hline
$V$ & The total value\\
\hline
$L,U$ & lower bound and upper bound of efficiency\\
\hline
$\rho$ & efficiency threshold\\
\hline
$V$ & The total value\\
\hline
$\lambda$ & a system parameter\\
\hline
$T_i$ & time stage\\
\hline
$f$ & submodular value function\\
\hline
\end{tabular}
\\
\caption{Notations}
\end{table}

>>>>

Mobile crowdsensing is a novel application paradigm that utilizes mobile devices to collect, analyze, and share their local information~\cite{ganti2011mobile,lane2010survey}. It usually consists of a service provider, service requesters, and mobile device users. The service provider (a.k.a., the crowdsensing platform), which usually resides in the cloud, recruits participants from mobile device users to upload their sensing data, and then provides services to service requesters based on the collected information. A wide variety of applications has emerged in recent years, including NoiseTube~\cite{maisonneuve2009noisetube} and Ear-phone~\cite{rana2010ear} for noise monitoring, SignalGuru~\cite{koukoumidis2011signalguru} and CrowdAtlas~\cite{wang2013crowdatlas} for traffic monitoring, and CrowdPark~\cite{yan2011crowdpark}, Parknet~\cite{mathur2010parknet} for finding on-street parking spots.

However, a well running crowdsensing application needs massive data contributed by the participants to ensure the service quality. Since participating in crowdsensing tasks requires the participants to devote resource consumptions of their smartphones, participants are usually reluctant to share their sensing capabilities(\eg, \cite{Kawajiri:2014:SCI:2632048.2636064,Fan:2015:PTT:2789168.2795179,Karaliopoulos:2016:FLE:2942358.2942369}. Thus, it is necessary to design an incentive mechanism to compensate the participants. According to different settings of scenarios, two cases are often discussed, \ie, offline setting and online setting. Researches on incentive mechanism designs, such as~\cite{yang2012crowdsourcing,koutsopoulos2013optimal}, are usually based on offline scenarios, where participants are present simultaneously while the online scenarios are more common in practice, where participants arrive and leave dynamically. Designing an incentive mechanism in online scenarios is much more complicated, due to the lack of future information. Besides, it brings challenges in the realization of strategy-proofness, since participants may misreport their arrival or departure time in order to gain higher benefits. Here, intuitively, strategy-proofness means that one can maximize her benefit by truthfully revealing her private information (\eg, arrival time, departure time, or sensing cost).

@@

We note that most existing works on online mechanism design only consider flat values, \ie, the value of each participant's contributed data is fixed during her presence. However, in many time sensitive applications (\eg, real-time traffic or noise monitoring~\cite{Chon:2014:SWP:2632048.2636066,Ji:2016:USB:2971648.2971735,Zappatore:2016:CAM:2851613.2851699,Cherian:2015:PPG:2809695.2817881}), the participants usually have time-discounting values, \ie, the value of each participant's contribution decreases as time goes by~\cite{babaioff2009secretary, wu2014strategy}. The time-discounting property really complicates the mechanism design problem. For instance, it has been proved that no online algorithm can achieve a competitive ratio better than $\Omega(\textrm{log}n/\textrm{log}\,\textrm{log}n)$ for discounted secretary problem~\cite{babaioff2009secretary}. The time-discounting property of values will bring much more difficulty, especially on the strategy-proofness. In the most of the incentive mechanisms designed for online crowdsensing, the payment to a selected participant is based on her contributation. If she can cheat her type, such as arrival time or cost, she may be selected at different time. If this time is earlier than the time with truely report information, the value of this participant calculated by the platform will be higher than the true value. For the purpose of more reward, the participant may have more incentives to bid mendaciously.

@@

To address these challenges, we propose a budget feasible online incentive mechanism with time-discounting values. We first consider the case where the total value is the summation of each participant's value. We define the efficiency of a participant as her value divided by her cost. Since participants arrive dynamically, we take advantage of the efficiency information of those who have arrived (we call a sample set) to calculate a threshold, and use it to guide subsequent selections. The intuition of our design is to greedily choose participants with the highest efficiencies from the sample set, and calculate their average efficiency multiplying an increasing factor as a threshold. The increasing factor is used to prevent the participants from misreporting their arrival or departure time. We divide the total time into slots. At each time slot, we select participants with efficiencies higher than the threshold within the budget constraint, and then calculate their payments. The payment scheme is carefully designed to ensure strategy-proofness and individual rationality. We prove that our mechanism can achieve a constant competitive ratio compared with the optimal solution with full information. We next consider the case where the total value is a submodular function of the selected participants, which is a more general situation. We prove that the time and cost-truthfullness can still be guaranteed by the newly designed algorithms. The numerical results show that our proposed approach has superior performance to our benchmark mechanisms.
\subsection{Key Contributions}
The main contributions of this paper is listed as follows
\begin{itemize}
\item We design an online incentive mechanism for crowdsensing. In this process, participants arrive over time. Our mechanism is designed to take advange of their efficiency to select them and give them a payment.

\item As far as we know, we are the first to consider the time-discounting property of values. To address the potential new difficulty, we design a novel algorithm to calcuate a time-related threshold to select participants and determine their payment.

\item We think about two cases according to the value function. The value function in these two cases is additive and submodular, the latter is more general.
\end{itemize}
\subsection{Paper Organization}
The rest of the paper is organized as follows. We briefly review the related work in Section II. In Section III, We introduce the model of the budget feasible online mechanism problem with time-discounting values, and recall some important solution concepts. In Section IV, we present our design of a strategy-proof online  mechanism where the value function is the summation of each participant's value. In Section V, we consider the case where the value function submodular. In Section VI, we implement and evaluate our mechanism. Finally, we conclude this paper in Section VI.
%**********************************************************
%The key challenges in a budget feasible auction are how to persue the maximum value and balance incentive compatibility and the budget constraint. It gets harder when the participants arrive dynamicly. What is noticeable is that in existing works, the value of a specific participant is often fixed, \ie, the participant has a bid of uniform value during her presence in the auction, independent of when she is selected. But in some realms, such as applications intending to collect data by crowdsensng, which are always modeled as reverse auctions, the values of participants' contributed information decrease with time. The time discounting characteristic can make the problem more difficult. In this paper, we study a type of online reverse auction, where the participants compete to provide items or services with certain time discounting values. Then the provider gives some payment to the selected participants according to their bids. The objective is to obtain  the maximum total value and achieve strategy-proofness under a limited budget. It should be noted that for general utility functions, there is no truthful mechanism achieving a reasonable approximation ratio~\cite{singer2014budget}. In our paper, the total value of participants is simplified to the summation of their values at when they are selected.
%**********************************************************
%We present a formal methonology based on the mechanism design as an inventive method in the realm of crowdsensing. which is a new paradigm of applications that includes a platform and ubiquitous participants who hold mobile devices equipped with enhanced sensors~\cite{ganti2011mobile}. The platform recruits participants to upload sensing data and then compensate them some payment according to their value. It is always modeled as a reverse auction. When designing an incentive mechanism for crowdsensing, participants' value is often taken into account when determining the task allocation and the payment. But in existing work, this value of a specific participant is often fixed, \ie, the participants have a bid of uniform value to the platform during their presences in the auction. However in many crowdsensing applications, the value of participants is time discounting, decreasing with time in majority situations. Therefore in this paper, we consider a scenario, in which participants compete for being allocated tasks and then compensated some monetary payment, but her bidding value is changing over time.  The bid of each participant is her arrival time, departure time, her cost and value to the platform which diminishes with time. The objective is to design a strategy-proof mechanism and maximize the platform's gainning value with limited budget with respect to not only the time discounting values, but also the present time and cost of the participants.

@@

The budget feasible mechanism has been widely studied to address budget limited mechanism design problem~\cite{Zhao:2016:BOI:3001647.3001648,Balkanski:2015:MFA:2764468.2764505,Chan:2016:BFM:2936924.2936945,Goel:2014:CAB:2600057.2602851,Lee:2016:MRV:2940716.2940745,Lu:2015:IEG:2764468.2764500,Goel:2015:PCA:2799630.2757277}. Singer~\cite{singer2010budget} first designed a budget feasible mechanism for scenarios where the value function is submodular. Chen \et\cite{chen2011approximability} further proposed a truthful budget feasible mechanism. It achieves a competitive ratio of larger than $\frac{1}{9}$, which is better than previously best result 233.83. Nevertheless, these work also failed to consider the time-discounting property.
%Zhou \et\cite{zhou2008budget} modeled the budgeted bidding optimization problem as an online knapsack problem, where the threshold is calculated based on the fraction of capacity filled.

Furthermore, there are some loosely related works on online mechanism design~\cite{Naroditskiy:2013:ROM:2484920.2485023,Kesselheim:2015:SOM:2764468.2764487,Furuhata:2014:COC:2615731.2616027}, \eg,  pricing and resource allocation in cloud computing~\cite{Shi:2014:OAF:2591971.2591980}, allocating tasks with temporal constraints~\cite{nunes2015multi}, improving targeting to increase total revenue~\cite{Hummel:2015:ITI:2736277.2741079}, and dynamic resource bundling and VM provisioning in IaaS clouds~\cite{Zhang:2015:OAI:2796314.2745855}.

@@

\begin{table}[!hbp]
\caption{Notations}
\center
\begin{tabular}{cc}
\hline

Symbol & Description\\
\hline
$\mathbb{N}={1,2,...,n}$ & The participant set \\
% \hline
$B$ & The total budget\\
% \hline
$\theta_i$ & Type of participant $i$\\
% \hline
$a_i$ & arrival time of participant $i$\\
% \hline
$d_i$ & departure time of participant $i$\\
% \hline
$v_i$ & value of participant $i$\\
% \hline
$c_i$ & cost of participant $i$\\
% \hline
$\hat{\theta}_i$ & bid of participant $i$\\
% \hline
$\mathbb{T}=\{1,2,...,T\}$ & the time slot set\\
% \hline
$\beta$ & time-discounting factor\\
% \hline
$p_i$ & payment of participant $i$\\
% \hline
$\mathbb{S}$ & selected participant set\\
% \hline
$V$ & The total value\\
% \hline
$L,U$ & lower bound and upper bound of efficiency\\
% \hline
$\rho$ & efficiency threshold\\
% \hline
$V$ & The total value\\
% \hline
$\lambda$ & a system parameter\\
% \hline
$T_i$ & time stage\\
% \hline
$f$ & submodular value function\\
\hline
\end{tabular}
\\

\end{table}
